---
title: "R Notebook"
output: html_notebook
---

```{r include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load df}
load("df_results.Rda")
```

#Introduction

## Packages considered

For this local regression packages comparison, we had to find as mcu hpackages as possible about it.
We found __locpol__ function from __locpol__ package, __locfit__ from __locfit__ ( _need to check the behaviour of h_ ) and __locpoly__ from __KernSmooth__. We found other packages such as lpridge(lpepa), stats(loess/lowess), lokern(lokerns) but they missed some important features in order to be well compared with everything. As example lpepa stands for lp_epachnenikov and then is not using gaussian kernel; loess has no bandwidth argument but rather a span one which has a totally different way of working.

## Parameters considered

We first wanted to compare the methods for the same bandwidth and kernel (gaussian) to see if indeed the results were the same, without regards of smoothness of the function. \
We then looked for consistency of each methods, looking if indeed the error was decreasing to zero with an increasing number of point, depending on the noise induced.

## Functions/space(interval) considered



